A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-22 manuscript/supplemental.tex
fixed one compilation error

      For species with $n_{ij}>0$, the posterior distribution will depend on the values of $n_{ij}$ and $k_{ij}$. Here we are interested only in cases where $k_{ij}=0$. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$. As $n_{ij}$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}). The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \empH{Appendix S11}).

>>>>

      For species with $n_{ij}>0$, the posterior distribution will depend on the values of $n_{ij}$ and $k_{ij}$. Here we are interested only in cases where $k_{ij}=0$. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. For a pair of species which co-occurred at all 374 sites and was never observed to interact, the distribution for the \emph{Salix}-galler network would become $\bar\lambda_{ij}$=1.27 $\times$ 10$^{-2}$, var($\lambda_{ij}$)=1.82 $\times$ 10$^{-5}$. As $n_{ij}$ decreases, the distribution widens and moves away from the origin (Fig.~\ref{Salix_pdfs}). The 95\% credible interval for hypothetical \emph{Salix}-galler pairs widened from (0.006, 0.022) if the pair co-occurred at all sites to (0.013, 0.049) if they co-occurred at none (Table~\ref{credints}, \emph{Appendix S11}).
